Appendix 1: Preregistered analysis with simulated data

### 2025-06-11 preregistration_code.Rmd
changing labels for bd04

table1 <-
  tbl_summary(
    data = data %>% 
      rename(
      Gender =  de01,
      Age = de02,
      DonationEligibility = bd01,
      DonationCount = bd02,
      DonationCountLast2years = bd03,
      DaysFromLastDonation = bd04 
    ),
    include = c(
      Age,
      DonationEligibility,
      DaysFromLastDonation,
      DonationCount,
      DonationCountLast2years
      ),
    by =  Gender,
     statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", all_categorical() ~
    "{n} ({p}%)")

>>>>

```{r}
table1 <-
  tbl_summary(
    data = data %>% 
      rename(
      Gender =  de01,
      Age = de02,
      DonationEligibility = bd01,
      DonationCount = bd02,
      DonationCountLast2years = bd03,
      WeeksFromLastDonation = bd04 
    ),
    include = c(
      Age,
      DonationEligibility,
      WeeksFromLastDonation,
      DonationCount,
      DonationCountLast2years
      ),
    by =  Gender,
     statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", all_categorical() ~
    "{n} ({p}%)")
